How kids code and how we know it:\\An exploratory study in the Scratch project repository

### 2016-04-15 Paper/paper.tex
Updated abstract and keywords

\maketitle
\begin{abstract}
Recently, block-based programming languages like Alice, Scratch and Blockly have become popular tools for programming education. There is substantial research showing that block-based languages are suitable for early programming education. But do block-based programs suffer from code clones \emph{smelly} too? In a recent controlled experiment, we found that code clones in Scratch indeed hamper novice Scratch programmers. In this paper we explore how commonly code clones occur in Scratch. To that end we have scraped Scratch public repository and retrieved 250.000 programs. We have analyzed three types of clones within those programs': clones of entire scripts within sprites, clones of entire between sprites, and cloned conditions. We find that those clones occur in ... of programs.
\end{abstract}

@@

\keywords{keywords}

>>>>

\maketitle
\begin{abstract}
Block-based programming languages like Scratch, Alice and Blockly are becoming increasingly common as introductory languages in programming education. There is substantial research showing that those visual programming environments are suitable for teaching programming concepts. In this paper we explore the characteristics of Scratch programs. To that end we have scraped the Scratch public repository and retrieved 250.000 projects. We present an analysis of those projects in terms of complexity, used abstractions and programming concepts, and coding style. We found that programming abstraction concepts like functions are not commonly used. We further investigate the presence of code smells and bad programming practices, including code duplication, dead code, long method and large class smells. Our findings indicate that Scratch programs suffer from code smells and especially code duplication.
\end{abstract}

@@

\keywords{Scratch, programming practices, code smells, static analysis}
